\documentclass[resmargin, centered, 10pt]{../res}
%Packages
	\usepackage{array,ragged2e} %Tabular formating
	\usepackage[pdfpagemode=FullScreen, colorlinks=true, linkcolor=black,  urlcolor=black]{hyperref} 
	\usepackage{fancyhdr}
	\usepackage[margin=1c m]{geometry}
	% allow hyphenation (was disabled)
	% \usepackage[none]{hyphenat} %To stop hyphenation
	\usepackage{enumitem}
	\usepackage{multicol}
	\usepackage{printlen} %for printing measurements
	\usepackage{xcolor}

%Dimensions, Settings & Variables
	\textwidth=16cm
	\textheight=26cm
%	\itemsep=0in	
	%\parsep=0in
	\setlength{\columnseprule}{1pt} %For multicols
	\renewcommand{\familydefault}{\sfdefault}
	
%CuLi
	\def \fullwidth{\textwidth}
	\def \subwidth{13.5cm}
	\def \halfwidth{6.5cm}
	\def \titlewidth{4.25cm}

	\newcommand{\tab}[1][1cm]{\hspace*{#1}} 
	\newcommand{\bref}[2]{\href{#1}{\color{black}\underline{\smash{#2}}}} %custom link command
	\newcommand{\loose}{\vspace{0.35cm}}
	\newcommand{\tight}{\vspace{-0.15cm}}
	\newcommand{\tighter}{\vspace{-0.5cm}}
	\newcommand{\subtext}[1]{\tab[0.5cm] \parbox{\dimexpr\fullwidth-0.5cm\relax}{#1}}
	\newcommand{\subtitle}[1]{\vspace{-1cm} ~ \newline  \emph{\subtext{#1}}}
	
\begin{document}
\name{
	KIRKWOOD P. DONAVIN -- COACH
}
% \tagline{Former data scientist -- Passionate about mathematics \& education}
\address{
	\begin{centering}
		\begin{tabular}{c | c | c | c}
			\href{mailto:kirkwood.donavin@gmail.com}{Kirkwood.Donavin@Gmail.com} &
			(801) 554-6834 &
			\bref{https://www.linkedin.com/in/kirkwood-donavin}{LinkedIn.com/in/Kirkwood-Donavin} & \bref{https://github.com/kdonavin}{GitHub.com/KDonavin}
		\end{tabular} 
	\end{centering}
}

\begin{resume}
% tighten itemize spacing
\setlist[itemize]{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
% slightly reduce font size for the resume body to help fit on one page
\small
    
\fullline

\section{SUMMARY}

EDIT Enthusiastic about mountain sports: trail running, summiting, mountaineering, ski touring, ski resort days with buddies, skate skiing, multi-pitch trad routes, climbing gym days with a pal, all-mountain bike riding. Experienced coach with a passion for helping others achieve their fitness and performance goals. Strong background in training plan development, technique analysis, and motivation strategies. Excellent communication skills and ability to build rapport with athletes of all levels.

\loose
\fullline

\section{EXPERIENCE}

\title{Track Coach, RRCA Level I}
\employer{SLC Track Club}
\dates{Feb 2022 -- Present}
\location{Salt Lake City, UT}
\begin{position}
	\begin{itemize}
		\item \textbf{Coaching} adult athletes through a pre-planned weekly workout and collaborating with the SLCTC coaching team
		\item \textbf{Workouts} vary from speed intervals, fartleks, tempo runs, and hill repeats.
		\item \textbf{Mentor Athletes} on training plans, pre-race ritual, form, recovery, and injury prevention
	\end{itemize}
\end{position}

\title{Mechanics Instructor}
\employer{The Bicycle Collective}
\dates{May 2025 -- Present}
\location{Salt Lake City, UT}
\begin{position}
	Instructor for the Bicycle Collective's community education program. Involved in course planning, as well as instruction or aiding co-instructors. \textbf{Courses Offered:} Drivetrains, Brakes (rim \& rotor), Bearing Systems, Tubeless Tires, Wheels, Suspension Systems
\end{position}


\loose
\fullline

\section{EDUCATION}

\textbf{Course Highlights}: Outdoor Leadership, Wilderness First Aid, Rec. Avalance Safety I \& II (American Avalance Institute)

\textbf{M.S. of Applied Economics -- May 2015 -- Montana State University --  Bozeman, MT}

\subtext{
	\textbf{Thesis}: 
	\bref{https://www.slideshare.net/slideshow/embed\_code/key/K6qYsOYvj9u5Ab}{The Welfare Impacts of Engineers Without Borders in Western Kenya}
}

\textbf{B.A of International Relations -- May 2011 -- Cornell College -- Mount Vernon, IA}

\loose
\fullline

\section{AWARDS}

\begin{multicols}{2}
\begin{itemize}
    \item NCAA DIII All-American (Mile Race, 3rd Place, 2011)
	\item Overall-Series Champion -- Cirque Series -- Sport Division -- 2021
	\item 2nd Place Overall-Series -- Wasatch Trail Series (Short Course) -- 2021
	\item 2011 Iowa Intercollegiate Athletic Conference (IIAC) MVP in Track \& Field
    \item 6x IIAC Champion (Events: 800m, 1500m, Mile, DMR; 2010 \& 2011 track seasons)
	\item 2011 Sportsman of the Year -- Cornell College
    \item 3x School Record Holder -- Cornel College (Events: 4x800m, DMR, Mile)
\end{itemize}
\end{multicols}

\end{resume}
\end{document}
