\documentclass[resmargin, centered, 10pt]{../res}
%Packages
	\usepackage{array,ragged2e} %Tabular formating
	\usepackage[pdfpagemode=FullScreen, colorlinks=true, linkcolor=black,  urlcolor=black]{hyperref} 
	\usepackage{fancyhdr}
	\usepackage[margin=1c m]{geometry}
	% allow hyphenation (was disabled)
	% \usepackage[none]{hyphenat} %To stop hyphenation
	\usepackage{enumitem}
	\usepackage{multicol}
	\usepackage{printlen} %for printing measurements
	\usepackage{xcolor}

%Dimensions, Settings & Variables
	\textwidth=16cm
	\textheight=26cm
%	\itemsep=0in	
	%\parsep=0in
	\setlength{\columnseprule}{1pt} %For multicols
	\renewcommand{\familydefault}{\sfdefault}
	
%CuLi
	\def \fullwidth{\textwidth}
	\def \subwidth{13.5cm}
	\def \halfwidth{6.5cm}
	\def \titlewidth{4.25cm}

	\newcommand{\tab}[1][1cm]{\hspace*{#1}} 
	\newcommand{\bref}[2]{\href{#1}{\color{black}\underline{\smash{#2}}}} %custom link command
	\newcommand{\loose}{\vspace{0.35cm}}
	\newcommand{\tight}{\vspace{-0.15cm}}
	\newcommand{\tighter}{\vspace{-0.5cm}}
	\newcommand{\subtext}[1]{\tab[0.5cm] \parbox{\dimexpr\fullwidth-0.5cm\relax}{#1}}
	\newcommand{\subtitle}[1]{\vspace{-1cm} ~ \newline  \emph{\subtext{#1}}}
	
\begin{document}
\name{
	KIRKWOOD P. DONAVIN -- EDUCATOR
}
% \tagline{Former data scientist -- Passionate about mathematics \& education}
\address{
	\begin{centering}
		\begin{tabular}{c | c | c | c}
			\href{mailto:kirkwood.donavin@gmail.com}{Kirkwood.Donavin@Gmail.com} &
			(801) 554-6834 &
			\bref{https://www.linkedin.com/in/kirkwood-donavin}{LinkedIn.com/in/Kirkwood-Donavin} & \bref{https://github.com/kdonavin}{GitHub.com/KDonavin}
		\end{tabular} 
	\end{centering}
}

\begin{resume}
% tighten itemize spacing
\setlist[itemize]{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}
% slightly reduce font size for the resume body to help fit on one page
\small
    
\fullline

\section{SUMMARY}

Former data scientist with 8 years of industry experience looking to switch careers into education. Classroom and tutoring experience spanning K–12 and college levels. Comfortable teaching Arithmetic, Algebra, Geometry, \& Calculus. Skilled at executing curriculum plans, creating engaging lesson materials, and communicating effectively with students, parents, and colleagues.

\loose
\fullline

\section{EXPERIENCE}

\title{Mechanics Instructor}
\employer{The Bicycle Collective}
\dates{May 2025 -- Present}
\location{Salt Lake City, UT}
\begin{position}
	Instructor for the Bicycle Collective's community education program. Involved in course planning, as well as instruction or aiding co-instructors. \textbf{Courses Offered:} Drivetrains, Brakes (rim \& rotor), Bearing Systems, Tubeless Tires, Wheels, Suspension Systems
\end{position}

\title{Track Coach, RRCA Level I}
\employer{SLC Track Club}
\dates{Feb 2022 -- Present}
\location{Salt Lake City, UT}
\begin{position}
	\begin{itemize}
		\item \textbf{Coaching} adult athletes through a pre-planned weekly workout and collaborating with the SLCTC coaching team
		\item \textbf{Workouts} vary from speed intervals, fartleks, tempo runs, and hill repeats.
		\item \textbf{Mentor Athletes} on training plans, pre-race ritual, form, recovery, and injury prevention
	\end{itemize}
\end{position}

\title{Grad. Teaching \& Research Asst.}
\employer{Montana State U.}
\dates{Aug 2013 -- May 2015}
\location{Bozeman, MT}
\begin{position}
Assistant to MSU faculty in Agricultural Finance, Agricultural Marketing, and Development Economics. Supported teaching and research duties including grading, assignment design, literature collection, and data gathering.

\begin{itemize}
    \item \textbf{Grading} 400+ essays and homework assignments across undergraduate courses
    \item \textbf{Course Material Design}: Designed 2 assignments for a Development Economics course
    \item \textbf{Literature Review}: Collected and organized 40+ journal articles on statistics education and pedagogy
    \item \textbf{Data Collection}: Gathered raw price data from over 15 Montana grain elevators for related research projects
\end{itemize}
\end{position}

\title{Math Instructor}
\employer{Mathnasium}
\dates{Feb 2013 -- Jul 2013}
\location{Salt Lake City}
\begin{position}
Tutored small groups (2--5 students) ages 6--18 using individualized Mathnasium curriculum as an extracurricular supplement to regular mathematics instruction.
\begin{itemize}
	\item \textbf{Lesson Execution} using Mathnasium curriculum aligned to each student’s learning plan and tracked progress
	\item \textbf{Dynamic 1-1 Instruction} for a range of abilities and ages
	\item \textbf{Parent Communication} weekly updates on student progress and areas for improvement
\end{itemize}
\end{position}

\title{Freelance Private Tutor}
\employer{Self-Employed}
\dates{Jan 2013 -- Jul 2013}
\location{Salt Lake City}
\begin{position}
	Provided one-on-one and small-group tutoring in Calculus, Algebra, and GRE quantitative preparation for students at the high-school and college levels.
	\begin{itemize}
		\item \textbf{Lesson Planning:} to target student weaknesses in specific math topics
		\item \textbf{Standardized Exams:}Prepared students for standardized exams with focused quantitative strategies
	\end{itemize}
\end{position}

\title{Math Tutor}
\employer{Westminster College}
\dates{Jan 2012 -- Dec 2012}
\location{Salt Lake City}
\begin{position}
Tutored groups of 1--3 college students in College Algebra, Statistics, and Single-Variable Calculus; assisted with homework, exam preparation, and conceptual understanding.
\end{position}

\loose
\fullline

\section{EDUCATION}

\textbf{Course Highlights}: Single/Multivar Calc, Discrete Math, Linear Algebra, Math Stats, Prob Theory, Real Analysis, Mathematical Econ

\textbf{M.S. of Applied Economics -- May 2015 -- Montana State University --  Bozeman, MT}

\subtext{
	\textbf{Thesis}: 
	\bref{https://www.slideshare.net/slideshow/embed\_code/key/K6qYsOYvj9u5Ab}{The Welfare Impacts of Engineers Without Borders in Western Kenya}
}

\textbf{B.A of International Relations -- May 2011 -- Cornell College -- Mount Vernon, IA}

\end{resume}
\end{document}
